FoRTE baseline

### 2019-03-26 analysis/paper/paper.Rmd
Flesh out paper outline

@@

>>>>

# Outline

- **Introduction**
    - Why we need models?
        - Forests are important, for C sequestration, other ecosystem services
        - Policy decisions related to forests depend on future projections
        - We need models to make future projections
    - What kinds of models are out there?
        - Traditional: "Big leaf" models
            - Needed to be simple to run on old computers
            - Don't need as much data
            - ...but they fail to capture important processes, which matter not only for accurate predictions about C cycle, but also because they are processes we care about (habitat, forestry, tourism, etc.)!
        - Individual-based models
            - Much more detailed, but harder to run, and need much more data.
            - Trade-off between complexity and accuracy.
        - Cohort-based models like ED2 as a middle ground?
    - How much complexity do we need to accurately model ecological succession?
        - Lots of existing work on parameteric uncertainty (e.g. Dietze, Raczka, others).
        - Less on structural uncertainty -- i.e. not just what coefficients do we use, but what _equations_, and more generally, what _processes_ do we even consider?
    - What are the processes that drive succession of ecological communities?
        - Competition for light
        - Competition for nutrients
        - Competition for water?
        - Others?
        - Brief review of community/ecosystem ecology of the Upper Midwest
    - Guiding questions:
        - Which of these processes do we need to be able to accurately model what happens ("community succession and C cycle dynamics") to Midwestern forests?
        - What is the cost of considering these processes, in terms of additional parameteric uncertainty?
        - What are the relative contributions of parameteric uncertainty (data limitation) vs. structural uncertainty (theoretical limitation?)?
    - Study overview:
        - ED with factorial combination of submodels
        - Ensemble analysis to look at parameter uncertainty
- **Methods**
    - Site description
    - ED2 model description
        - Common features
        - Submodel descriptions (in brief; more details in appendices)
            - Two-stream RTM
            - Multiple-scatter RTM
            - Finite canopy radius model
            - Trait plasticity scheme
            - N limitation (?)
    - Data sources
        - TRY data
        - Other data? FIA? Remote sensing?
    - Modeling workflow (PEcAn, etc.)
    - Data analysis
        - Structural vs. parametric uncertainty
        - Comparison against "reality"
- **Results**
    - Summary:
        - LAI time series with uncertainties, faceted by model structure
    - Structural uncertainty details
        - Fig: RTM comparison (Radiation profile)
        - Fig: Crown model comparison
        - Fig: Trait plasticity?
    - Uncertainty analysis
        - Which parameters contribute the most uncertainty?
        - Structural vs. parameteric uncertainty
- **Discussion**
    - (Generally, mirrors results section)
    - Overview of major findings
    - Ecological implications of structural uncertainty
    - Implications of uncertainty analysis for future data collection and model development
    - Future directions: Predicting disturbance response

@@

## General outline
